\hypertarget{page14_FullBodyBipedIK}{}\section{Full\+Body\+Biped\+IK}\label{page14_FullBodyBipedIK}
{\bfseries -\/ Can I use F\+B\+B\+IK to create animation clips for my character, how does it save the animation clips?} ~\newline
F\+B\+B\+IK is not designed for animation authoring, but for runtime animation modification, meaning it will run on top of whatever animation you have to provide you more flexibility and accuracy when interacting with ingame objects and other character. ~\newline
For example if your character is climbing a wall, you can apply Full Body IK on top of it to make sure your hands and feet always remain fixed to the ledges. ~\newline
That doesn\textquotesingle{}t mean you can\textquotesingle{}t write a system that records the animation that has been modified with F\+B\+B\+IK to create customised animation clips for different characters.

{\bfseries -\/ Hope that this will not only work with a special 3d program. Is there any information on how to export from a 3D animation package?} ~\newline
Final IK has nothing to do with any 3D animation packages. You would animate and export your animation clips just like you are doing it now, ~\newline
the IK components will just provide a library of possibilities for extending, modifying and characterising those animations. ~\newline
The primary function of Full Body IK is not providing a rig for creating animations in Unity from scratch, it is modifying the existing animations ~\newline
and retargeting specific body parts to match the dynamic realtime environment. ~\newline
It will dramatically reduce the amount of animation work you will have to do for your game.

{\bfseries -\/ This system actually allows to have completly non-\/animated animations that are run only from scripts right? } ~\newline
 Yes.

{\bfseries -\/ Compared to mocap, what can I expect with the I\+K-\/based animations from your system?} ~\newline
IK animation can not be compared to mocap, ideally they should work together, not replace each other. ~\newline
Procedural IK only takes you so far. If you are aiming for real A\+AA quality and you want to compare your game with the Assassins Creed or Max Payne 3, you\textquotesingle{}ll still need top notch mocap base animation.

{\bfseries -\/ Does Mecanim work better than Legacy in conjunction with Final IK or if it doesn\textquotesingle{}t matter which system to use all?} ~\newline
It does not matter at all, go with what you prefer.

{\bfseries -\/ Can we tween in and out of an IK\textquotesingle{}d pose? } ~\newline
Yes, we can!

{\bfseries -\/ Can I remove/add limbs to or from F\+B\+B\+IK?} ~\newline
No, not yet at least. In the current beta version, you can\textquotesingle{}t detach a limb A\+ND continue using Full Body IK. You can disable F\+B\+B\+IK and then detach the limb (which is fine in 99\% of the use cases because the character would usually just die), but you can\textquotesingle{}t use the solver after you have deleted the bones. If there is a way to get rid of the limb geometry, but maintain the bones, then there is no problem, but remember, no removing the bones. I hope to overcome that limitation in the full release. Same goes for adding extra limbs. You can still use a seperate C\+C\+D/\+F\+A\+B\+R\+IK or Limb IK component on the extra limb if you need to.

{\bfseries -\/ Can it actually work perfectly upside down?} ~\newline
Yes it works upside down, you can rotate the characters however you like and still use IK.

{\bfseries -\/ Does Final IK allow you to rig a 3D mesh that does not have any bones?} ~\newline
No, it needs to have bones and skinning.

{\bfseries -\/ Can I use Rotation Limits with Full Body Biped IK?} ~\newline
Rotation Limits can be used with the C\+CD, F\+A\+B\+R\+IK and Aim IK components, F\+B\+B\+IK has it\textquotesingle{}s own dedicated constraints that keep the limbs bending in the right direction and the spine from collapsing into itself.\hypertarget{page14_Misc}{}\section{Misc}\label{page14_Misc}
{\bfseries -\/ Do you think F\+A\+B\+R\+IK can be used for simulating hair or a piece of cloth on a biped?} ~\newline
Yes F\+A\+B\+R\+IK theoretically can be used to simulate cloth or hair. But in a future release, I\textquotesingle{}m planning to include Particle IK, which would probably be more suitable for this, as it is the de facto standard for those kinds of simulations.

{\bfseries -\/ Does Final IK work with 2D?} ~\newline
While you can constrain most of the solvers to 2D with Rotation Limits, there are no dedicated 2D solvers yet.\hypertarget{page14_Pricing}{}\section{Pricing}\label{page14_Pricing}
{\bfseries -\/ Do you have any plans to go for Asset Store\textquotesingle{}s \char`\"{}\+Daily Deals\char`\"{}?} ~\newline
 Yes, but not in the near future, at least not until it\textquotesingle{}s out of the Beta. ~\newline
 If I did, the ones who took the risk to buy the unrated, unreviewed initial Beta version would feel scammed. They need to get a good head start with this.

{\bfseries -\/ Will you increase the price when Final IK reaches 1.\+0?} ~\newline
 I don\textquotesingle{}t know yet, sorry  